### 2024-06-04 thesis/input_files/data_exploratory.tex
cleaned all problems and warnings

% - Explain how data has been retrieved.

% - Data provider Energycharts(entsoe retrieves its data)

% - Explain the ETL(Extract Transform Load) pipeline
% I set up.

% - Explore data in order to get useful insights for
% how to tune the models to get the most of them.

% - correlation between temperatures and load, wind speeds and load

% - Split train and test dataset
% Explain carefully why it is important to carry
% out an out of sample test and not in sample.
% In sample test involves look ahead bias because we are
% fitting the model on the data we want to predict,
% thus it overfits on the data considered but it does
% not generalize well.

@@

\section{GEFCom2014}
The first class of datasets we identified are the ones from the GEFCom2014 competition. The data is freely hosted on Dr.\ Hong's blog \cite{hong2016probabilistic}.
The main reason is that, these datasets are considered an excellent test case for comparing predictive models between the EF community. Additionally, the scores of the competing models are freely available, this enables us to carry out a clean and transparent comparative study.
The GEFCom2014 consisted of four tracks: price, load, wind power and solar power forecasting. 
The GEFCom2014 folder contains a zip file for each of the four tracks.
We provide forecasts for the load and price quantities.
\\
\subsection{GEFCom2014 price track}
In the price forecasting track, the goal was to predict the electricity price for the next 24 hours of a single zone. 
The data can be found in the GEFCom2014-P\_V2 zip file alongside a set of instructions and the benchmark forecasts.
This data consists of time series for the locational marginal price, for the zonal load and for the system load. The data covers the time interval ranging from the $1^{st}$ of January 2011 to the $15^{th}$ of June 2013, see Figure \ref{fig:price_track_fig1}.\ 
Additionally, as the competition went on, the real observed data of the previous tasks were made available.
The 15 target days ordered by task number are: 16/06/2013, 17/06/2013, 24/06/2013, 04/07/2013, 09/07/2013, 13/07/2013, 16/07/2013, 18/07/2013, 19/07/2013, 20/07/2013, 24/07/2013, 25/07/2013, 07/12/2013, 08/12/2013, 17/12/2013. 
The first three tasks were designed for testing, they did not count for the competition.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/price_track_fig1.png}
    \caption{Price track GEFCom2014}
    \label{fig:price_track_fig1}
\end{figure}
\subsubsection{EDA}
In exploring this data we started off by plotting the time series of the zonal prices alongside with the total load and zonal load, see Figure \ref{fig:price_track_fig1}.
After that, we plotted the scatter plot for inspecting the correlation between the predictors and the dependent variables, Figure \ref{fig:gefcom_zonal_price_vs_zonal_load} and Figure \ref{fig:gefcom_zonal_price_vs_total_load}. From these visualisations, we can see their goodness for predicting zonal prices since there exists a clear correlation between the candidate predictors and the target variables.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/gefcom_zonal_price_vs_zonal_load.png}
    \caption{Zonal price versus zonal load of GEFCom2014}
    \label{fig:gefcom_zonal_price_vs_zonal_load}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/gefcom_zonal_price_vs_total_load.png}
    \caption{Zonal price versus total load of GEFCom2014}
    \label{fig:gefcom_zonal_price_vs_total_load}
\end{figure}

\subsection{GEFCom2014 load track}
In the load track, contestants were asked to provide one month ahead hourly probabilistic forecasts on a rolling basis for 15 consecutive rounds. To get started, in the first round, organisers provided 69 months of hourly load data (from 01/01/2005 to 30/10/2010) and 117 months of hourly temperature data (from 01/01/2001 to 30/10/2010). 
As for the price track, the true observed data from the previous track were made available as the competition progressed.
\\
The data for load forecasting is contained in the GEFCom2014-L\_V2 zip file. Within this subfolder, we have a txt file with the competition instructions and 15 subfolders one for each of the consecutive tasks. For each of those we have the prediction of the competition benchmark model and the train file upon which we will fit our model.
Any data from the various task folders are shifted by one month between each other.
Also in this track, the first three tasks do not count towards the ranking of the various algorithms.
\\
In order to compare our model performance with the winning entries of the GEFCom2014 load competition, we will refer to the Provisional\_Leaderboard\_\-V2.csv file contained also in the GEFCom2014 Data directory.
% Notice a quick premise, within this xsls file the authors opted for various scores to compare the entries performance. This choice was motivated by the need 
% to give a proportial weight to each task when averaging between them; that is in order to not penalise too much the tasks with higher point spreads. Furthermore, additional factors such as frequency of benchmark outperformance, and robustness and clarity in methodology explaination.
\\
The pinball scores for the load track are stored inside the subtab L-score-0/L-score-2 of Provisional\_Leaderboard\_V2.
\subsubsection{EDA}
We applied the same kind of EDA to the GEFCom load data. Figure \ref{fig:gefcom_load_historical} depicts the historical load while Figure \ref{fig:gefcom_w_avg_historical} reports the historical weather temperature. Finally, Figure \ref{fig:gefcom_load_vs_w_avg} shows the scatter plot between the load and the weather.
These plots motivate the selection of weather temperature as one of the predictors for the load.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/gefcom_load_historical.png}
    \caption{Historical load of GEFCom2014}
    \label{fig:gefcom_load_historical}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/gefcom_w_avg_historical.png}
    \caption{Historical weather of GEFCom2014}
    \label{fig:gefcom_w_avg_historical}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/gefcom_load_vs_w_avg.png}
    \caption{Load versus weather of GEFCom2014}
    \label{fig:gefcom_load_vs_w_avg}
\end{figure}

@@

\subsubsection{EDA}
Following we report the EDA plots alongside with insights that can be extracted from them. We choose to focus the following analysis on the Swiss data only, given that the plots for the German data are pretty similar.
To get started we visualise the historical load data in Figure \ref{fig:CH_historical_load_2021}. As expected, electricity load exhibits a seasonal pattern with highs in the winter and lows during the summer season.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_historical_load_2021.png}
    \caption{Switzerland historical load (2021)}
    \label{fig:CH_historical_load_2021}
\end{figure}
Next, we built scatter plots of the independent continous variables against the load as means of visualising correlation between them.
Figure \ref{fig:CH_load_vs_temperature_2021} plots load against temperatures while Figure \ref{fig:CH_load_vs_wind_speed_2021} depicts load against wind speed. From these plots, we can clearly see there exists a relationship that ties wind speeds and temperatures to load.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_load_vs_temperature_2021.png}
    \caption{Load versus temperature for Switzerland (2021)}
    \label{fig:CH_load_vs_temperature_2021}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_load_vs_wind_speed_2021.png}
    \caption{Load versus wind speed for Switzerland (2021)}
    \label{fig:CH_load_vs_wind_speed_2021}
\end{figure}

@@

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_day_of_week_boxplot_2021.png}
    \caption{Load versus day of week boxplot for Switzerland (2021)}
    \label{fig:CH_day_of_week_boxplot_2021}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_is_holiday_boxplot_2021.png}
    \caption{Load versus day type boxplot for Switzerland (2021)}
    \label{fig:CH_is_holiday_boxplot_2021}
\end{figure}

@@

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/CH_heatmap_2021.png}
    \caption{Switzerland load heatmap (2021)}
    \label{fig:CH_heatmap_2021}
\end{figure}

>>>>

@@

\section{GEFCom2014}
The first class of datasets we identified are the ones from the GEFCom2014 competition. The data is freely hosted on Dr.\ Hong's blog \cite{hong2016probabilistic}.
The main reason is that, these datasets are considered an excellent test case for comparing predictive models between the EF community. Additionally, the scores of the competing models are freely available, this enables us to carry out a clean and transparent comparative study.
The GEFCom2014 consisted of four tracks: price, load, wind power and solar power forecasting. 
The GEFCom2014 folder contains a zip file for each of the four tracks.
We provide forecasts for the load and price quantities.

\subsection{GEFCom2014 price track}
In the price forecasting track, the goal was to predict the electricity price for the next 24 hours of a single zone. 
The data can be found in the GEFCom2014-P\_V2 zip file alongside a set of instructions and the benchmark forecasts.
This data consists of time series for the locational marginal price, for the zonal load and for the system load. The data covers the time interval ranging from the $1^{st}$ of January 2011 to the $15^{th}$ of June 2013, see Figure \ref{fig:price_track_fig1}.\ 
Additionally, as the competition went on, the real observed data of the previous tasks were made available.
The 15 target days ordered by task number are: 16/06/2013, 17/06/2013, 24/06/2013, 04/07/2013, 09/07/2013, 13/07/2013, 16/07/2013, 18/07/2013, 19/07/2013, 20/07/2013, 24/07/2013, 25/07/2013, 07/12/2013, 08/12/2013, 17/12/2013. 
The first three tasks were designed for testing, they did not count for the competition.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/price_track_fig1.png}
    \caption{Price track GEFCom2014}
    \label{fig:price_track_fig1}
\end{figure}
\subsubsection{EDA}
In exploring this data we started off by plotting the time series of the zonal prices alongside with the total load and zonal load, see Figure \ref{fig:price_track_fig1}.
After that, we plotted the scatter plot for inspecting the correlation between the predictors and the dependent variables, Figure \ref{fig:gefcom_zonal_price_vs_zonal_load} and Figure \ref{fig:gefcom_zonal_price_vs_total_load}. From these visualisations, we can see their goodness for predicting zonal prices since there exists a clear correlation between the candidate predictors and the target variables.

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/gefcom_zonal_price_vs_zonal_load.png}
    \caption{Zonal price versus zonal load of GEFCom2014}
    \label{fig:gefcom_zonal_price_vs_zonal_load}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/gefcom_zonal_price_vs_total_load.png}
    \caption{Zonal price versus total load of GEFCom2014}
    \label{fig:gefcom_zonal_price_vs_total_load}
\end{figure}

\subsection{GEFCom2014 load track}
In the load track, contestants were asked to provide one month ahead hourly probabilistic forecasts on a rolling basis for 15 consecutive rounds. To get started, in the first round, organisers provided 69 months of hourly load data (from 01/01/2005 to 30/10/2010) and 117 months of hourly temperature data (from 01/01/2001 to 30/10/2010). 
As for the price track, the true observed data from the previous track were made available as the competition progressed.

The data for load forecasting is contained in the GEFCom2014-L\_V2 zip file. Within this subfolder, we have a txt file with the competition instructions and 15 subfolders one for each of the consecutive tasks. For each of those we have the prediction of the competition benchmark model and the train file upon which we will fit our model.
Any data from the various task folders are shifted by one month between each other.
Also in this track, the first three tasks do not count towards the ranking of the various algorithms.

In order to compare our model performance with the winning entries of the GEFCom2014 load competition, we will refer to the Provisional\_Leaderboard\_\-V2.csv file contained also in the GEFCom2014 Data directory.
% Notice a quick premise, within this xsls file the authors opted for various scores to compare the entries performance. This choice was motivated by the need 
% to give a proportial weight to each task when averaging between them; that is in order to not penalise too much the tasks with higher point spreads. Furthermore, additional factors such as frequency of benchmark outperformance, and robustness and clarity in methodology explaination.
\\
The pinball scores for the load track are stored inside the subtab L-score-0/L-score-2 of Provisional\_Leaderboard\_V2.
\subsubsection{EDA}
We applied the same kind of EDA to the GEFCom load data. Figure \ref{fig:gefcom_load_historical} depicts the historical load while Figure \ref{fig:gefcom_w_avg_historical} reports the historical weather temperature. Finally, Figure \ref{fig:gefcom_load_vs_w_avg} shows the scatter plot between the load and the weather.
These plots motivate the selection of weather temperature as one of the predictors for the load.

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/gefcom_load_historical.png}
    \caption{Historical load of GEFCom2014}
    \label{fig:gefcom_load_historical}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/gefcom_w_avg_historical.png}
    \caption{Historical weather of GEFCom2014}
    \label{fig:gefcom_w_avg_historical}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/gefcom_load_vs_w_avg.png}
    \caption{Load versus weather of GEFCom2014}
    \label{fig:gefcom_load_vs_w_avg}
\end{figure}

@@

\subsubsection{EDA}
Following we report the EDA plots alongside with insights that can be extracted from them. We choose to focus the following analysis on the Swiss data only, given that the plots for the German data are pretty similar.
To get started we visualise the historical load data in Figure \ref{fig:CH_historical_load_2021}. As expected, electricity load exhibits a seasonal pattern with highs in the winter and lows during the summer season.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_historical_load_2021.png}
    \caption{Switzerland historical load (2021)}
    \label{fig:CH_historical_load_2021}
\end{figure}
Next, we built scatter plots of the independent continous variables against the load as means of visualising correlation between them.
Figure \ref{fig:CH_load_vs_temperature_2021} plots load against temperatures while Figure \ref{fig:CH_load_vs_wind_speed_2021} depicts load against wind speed. From these plots, we can clearly see there exists a relationship that ties wind speeds and temperatures to load.

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_load_vs_temperature_2021.png}
    \caption{Load versus temperature for Switzerland (2021)}
    \label{fig:CH_load_vs_temperature_2021}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_load_vs_wind_speed_2021.png}
    \caption{Load versus wind speed for Switzerland (2021)}
    \label{fig:CH_load_vs_wind_speed_2021}
\end{figure}

@@

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_day_of_week_boxplot_2021.png}
    \caption{Load versus day of week boxplot for Switzerland (2021)}
    \label{fig:CH_day_of_week_boxplot_2021}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_is_holiday_boxplot_2021.png}
    \caption{Load versus day type boxplot for Switzerland (2021)}
    \label{fig:CH_is_holiday_boxplot_2021}
\end{figure}

@@

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/CH_heatmap_2021.png}
    \caption{Switzerland load heatmap (2021)}
    \label{fig:CH_heatmap_2021}
\end{figure}

### 2024-06-04 thesis/input_files/energymarket.tex
cleaned all problems and warnings

This chapter has two intents. Firstly, it summarises several concepts for the newcomers to the field of electricity markets. Secondly, it discusses trends and challenges in the power sector. Such developments motivate the need for robust and efficient forecasting techniques.

\section{Electricity distribution network}
Electricity is generated by power plants which transfer it over the so called transmission level. Then, through the transmission network, this energy is transported at a high voltage over long distances. Finally, the voltage is reduced and the energy is moved into the distribution network. Transmission lines carry electric power from stations to substations while distribution lines carry electricity from substations to load points such as businesses, industries and homes, see Figure \ref{electricity_network}.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/electricity_network.png}
    \caption{Electricity grid \cite{haben2021review}}
    \label{electricity_network}
\end{figure}

\section{Electricity markets}
Electricity markets have undergone rapid changes all over the world during the last three decades.
Before this revolution, the power sector was a natural monopoly. In particular, it was characterised by a high vertical integration and by very little market competition. Better technologies in transmission, generation and distribution are the reasons for such liberal shift. The rationale is simple, a competitive market promotes efficiency and stimulates technical innovation more than a monopoly does.
\\
During the 1990s, various wholesale electricity markets were established; for example in Chile, Great Britain, the Scandinivian block, Australia, New Zealand, the US and Canada. New participants, each with a specific task, entered the power market scenario.
\begin{itemize}
    \item Electricity generators produce electricity to be consumed.
    \item Electricity transmission owners 
    move high voltage electricity to electric utility companies whilst ensuring safe and reliable supply.
    \item Electricity grid operators are responsible for scheduling electricity over the transmission network in order to ensure supply demand balance.
    \item Electric utilities deliver power over local lines to consumers. 
    \item Retail energy suppliers purchase electricity in the wholesale market from electricity generators and resell it to consumers.
\end{itemize}
These functions are not mutually exclusive. That is, an entity can provide one or more of these services.

\subsection{The marketplace}
We can differentiate between two kinds of electricity markets: power pools and power exchanges. In power pools, generators bid the prices at which they are willing to produce at different volumes. Then, the market clearing price (MCP) is determined by intersecting the aggregated supply curve and the estimated demand, left panel Figure \ref{fig:pool_vs_echange}. Power pools are created on public initiatives of governments. Conversely, power exchanges are created through private agreements between generators, distributors and traders. This is the model followed by most of European countries.
The MCP in power exchanges is determined by the intersection of the aggregate supply curve and the aggregate demand curve, right panel Figure \ref{fig:pool_vs_echange}.
\\
It is worth to mention the two biggest power exchanges: Epex and NordPool. Epex operates throughout continental Europe. NordPool covers the nordic and baltic countries.
\\
Moreover, we can differentiate between two popular types of auctions: uniform-price/marginal and pay-as-bid/discriminatory. Within the uniform price setting, suppliers offering for less than the clearing price are paid that price. Analogously, consumers bidding more than the clearing price pay that price. On the other hand, in pay-as-bid auctions, suppliers are paid the exact price they bid for.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/pool_vs_echange.png}
    \caption{Pool market versus power echange \cite{weron2006modeling}}
    \label{fig:pool_vs_echange}
\end{figure}

@@

\subsection{Nodal and zonal pricing}
Grid configuration and physical limits on electricity lines may lead to congestion. Zonal market clearing pricing (ZMCP) and local marginal price (LMP) are two types of pricing schemes utilised to address this. The former is adopted in European contries while the latter is used in the United States, Figure \ref{fig:eu_zonal} and Figure \ref{fig:us_local}.
With zonal market clearing pricing, prices may differ between zones but are the same within the same area.
On the other hand, local marginal price is made up by summing the transmission congestion cost, generation marginal cost and the cost of marginal losses at different buses. Buses is where a electricity line or several lines are connected.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/eu_zonal.png}
    \caption[Zonal pricing in the EU]{Zonal pricing in the EU \citeW{eu_zonal}}
    \label{fig:eu_zonal}
\end{figure}

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/us_local.png}
    \caption[Local pricing for the US]{Local pricing for the US \citeW{us_local}}
    \label{fig:us_local}
\end{figure}

@@

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/electricity-production-by-source.png}
    \caption{Electricity production by source \cite{energy2023statistical}}    
    \label{fig:electricity_production_by_source}
\end{figure}

>>>>

This chapter has two intents. Firstly, it summarises several concepts for the newcomers to the field of electricity markets. Secondly, it discusses trends and challenges in the power sector. Such developments motivate the need for robust and efficient forecasting techniques.
\section{Electricity distribution network}
Electricity is generated by power plants which transfer it over the so called transmission level. Then, through the transmission network, this energy is transported at a high voltage over long distances. Finally, the voltage is reduced and the energy is moved into the distribution network. Transmission lines carry electric power from stations to substations while distribution lines carry electricity from substations to load points such as businesses, industries and homes, see Figure \ref{electricity_network}.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/electricity_network.png}
    \caption{Electricity grid \cite{haben2021review}}
    \label{electricity_network}
\end{figure}
\section{Electricity markets}
Electricity markets have undergone rapid changes all over the world during the last three decades.
Before this revolution, the power sector was a natural monopoly. In particular, it was characterised by a high vertical integration and by very little market competition. Better technologies in transmission, generation and distribution are the reasons for such liberal shift. The rationale is simple, a competitive market promotes efficiency and stimulates technical innovation more than a monopoly does.

During the 1990s, various wholesale electricity markets were established; for example in Chile, Great Britain, the Scandinivian block, Australia, New Zealand, the US and Canada. New participants, each with a specific task, entered the power market scenario.
\begin{itemize}
    \item Electricity generators produce electricity to be consumed.
    \item Electricity transmission owners 
    move high voltage electricity to electric utility companies whilst ensuring safe and reliable supply.
    \item Electricity grid operators are responsible for scheduling electricity over the transmission network in order to ensure supply demand balance.
    \item Electric utilities deliver power over local lines to consumers. 
    \item Retail energy suppliers purchase electricity in the wholesale market from electricity generators and resell it to consumers.
\end{itemize}
These functions are not mutually exclusive. That is, an entity can provide one or more of these services.

\subsection{The marketplace}
We can differentiate between two kinds of electricity markets: power pools and power exchanges. In power pools, generators bid the prices at which they are willing to produce at different volumes. Then, the market clearing price (MCP) is determined by intersecting the aggregated supply curve and the estimated demand, left panel Figure \ref{fig:pool_vs_echange}. Power pools are created on public initiatives of governments. Conversely, power exchanges are created through private agreements between generators, distributors and traders. This is the model followed by most of European countries.
The MCP in power exchanges is determined by the intersection of the aggregate supply curve and the aggregate demand curve, right panel Figure \ref{fig:pool_vs_echange}.

It is worth to mention the two biggest power exchanges: Epex and NordPool. Epex operates throughout continental Europe. NordPool covers the nordic and baltic countries.

Moreover, we can differentiate between two popular types of auctions: uniform-price/marginal and pay-as-bid/discriminatory. Within the uniform price setting, suppliers offering for less than the clearing price are paid that price. Analogously, consumers bidding more than the clearing price pay that price. On the other hand, in pay-as-bid auctions, suppliers are paid the exact price they bid for.

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/pool_vs_echange.png}
    \caption{Pool market versus power echange \cite{weron2006modeling}}
    \label{fig:pool_vs_echange}
\end{figure}

@@

\subsection{Nodal and zonal pricing}
Grid configuration and physical limits on electricity lines may lead to congestion. Zonal market clearing pricing (ZMCP) and local marginal price (LMP) are two types of pricing schemes utilised to address this. The former is adopted in European contries while the latter is used in the United States, Figure \ref{fig:eu_zonal} and Figure \ref{fig:us_local}.
With zonal market clearing pricing, prices may differ between zones but are the same within the same area.
On the other hand, local marginal price is made up by summing the transmission congestion cost, generation marginal cost and the cost of marginal losses at different buses. Buses is where a electricity line or several lines are connected.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/eu_zonal.png}
    \caption[Zonal pricing in the EU]{Zonal pricing in the EU \citeW{eu_zonal}}
    \label{fig:eu_zonal}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/us_local.png}
    \caption[Local pricing for the US]{Local pricing for the US \citeW{us_local}}
    \label{fig:us_local}
\end{figure}

@@

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/electricity-production-by-source.png}
    \caption{Electricity production by source \cite{energy2023statistical}}    
    \label{fig:electricity_production_by_source}
\end{figure}

### 2024-06-04 thesis/input_files/implementation.tex
cleaned all problems and warnings

This section is intended to explain and aid for reproducibility studies. Hereafter, the specific libraries used and the custom implementations are thoroughly documented.
\\
For the list of Python packages needed, see the requirement.txt file on \url{https://github.com/luca-pernigo/ThesisKernelMethods}\label{github_repo}.
% - indicate computer specifics
All experiments have been carried out on a 3.2 GHz 16GB Apple M1 Pro.

@@

\subsection{Trigonometric seasonality Box-Cox transformation ARMA errors trend and seasonal components}
The Tbats implementation is available at \href{https://github.com/intive-DataScience/tbats}{https://github.com/intive-Data-Science/tbatsx}.
In our application we specified as hyperparameters the length of seasons, that is, 24 for the daily seasonality and 168 for the weekly seasonality.

>>>>

This section is intended to explain and aid for reproducibility studies. Hereafter, the specific libraries used and the custom implementations are thoroughly documented.

For the list of Python packages needed, see the requirement.txt file on the \href{https://github.com/luca-pernigo/ThesisKernelMethods}{github repo}.
% - indicate computer specifics
All experiments have been carried out on a 3.2 GHz 16GB Apple M1 Pro.

@@

\subsection{Trigonometric seasonality Box-Cox transformation AR\-MA errors trend and seasonal components}
The Tbats implementation is available at \href{https://github.com/intive-DataScience/tbats}{https://github.com/intive-Data-Science/tbatsx}.
In our application we specified as hyperparameters the length of seasons, that is, 24 for the daily seasonality and 168 for the weekly seasonality.
